Effects of CHILDREN's programs

### 2020-02-24 paper.Rnw
ghj

          float.env = "sidewaystable")
# row.names(tableDispSumm) <- c("$Disp_t^n$", "$Disp_t^d$", "$Disp_t^a$", "$Y_t^n$", "$Y_t^d$", "$GDP_t$")
# colnames(tableDispSumm) <- c("$Corr(X_t, X_{t-1})$", "$\\sigma(X)$", "$\\frac{\\sigma(X)}{\\sigma(Y)}$", "$\\frac{\\sigma(X)}{\\sigma(GDP)}$")
# tableDispSumm <- xtable(tableDispSumm, caption = "Productivity dispersion: Summary statistics", digits = 3, align = "crccc")
# print(tableDispSumm, sanitize.text.function = function(x) {x}, caption.placement = "top")
@

>>>>

          float.env = "sidewaystable")
# row.names(tableDispSumm) <- c("$Disp_t^n$", "$Disp_t^d$", "$Disp_t^a$", "$Y_t^n$", "$Y_t^d$", "$GDP_t$")
# colnames(tableDispSumm) <- c("$Corr(X_t, X_{t-1})$", "$\\sigma(X)$", "$\\frac{\\sigma(X)}{\\sigma(Y)}$", "$\\frac{\\sigma(X)}{\\sigma(GDP)}$")
# tableDispSumm <- xtable(tableDispSumm, caption = "Productivity dispersion: Summary statistics", digits = 3, align = "crccc")
# print(tableDispSumm, sanitize.text.function = function(x) {x}, caption.placement = "top")
@
<<Partition, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=

partition_meals = readRDS("./ANALYSIS/Tables/PartitionMeals.4.Rds")
partition_trips = readRDS("./ANALYSIS/Tables/PartitionTrips.4.Rds")

colnames(partition_meals) <- c("Variable, Meals", "Mapping, Meals", "Information, Meals")
colnames(partition_trips) <- c("Variable, Trips", "Mapping, Trips", "Information, Trips")

xtable(partition_meals,
                               #digits = c(0, 0, 1, 1, 0, 0),
          caption = "Partition of outcomes, Meals"
          #align = "lmmm"
          )
#print(partition_meals, include.rownames = FALSE)

xtable(partition_trips,
                               #digits = c(0, 0, 1, 1, 0, 0),
          caption = "Partition of outcomes, Trips"
          #align = "lmmm"
          )
print(partition_meals, partition_trips, include.rownames = FALSE)
@
